Adopting agile in the large: motivations, success factors and challenges

### 2014-05-17 journal/article.tex
Figure for full study selection process

\item
RQ2: How do large scale agile transformations usually proceed; do
     transformations exhibit patterns?

@@

% --> Why are the preliminary searches done?

Before proceeding with the database search a number of preliminary searches were
performed. The purpose of the preliminary searches was to create a benchmark of
potentially relevant papers that should be matched by the actual database
search. We also wanted to list top ranked hits by trivial keywords that the
more complex final search string might miss. Initial searches were made using
keywords that were as general as possible, including ``agile transformation''
and ``large scale agile''. Additionally, a trial keyword search was done in the
selected databases (listed in table \ref{table:databases}) using the following
search string:

@@

The study selection process inlcuded three steps, each step refining the set of
selected papers. First a database search was used to gather an initial set of
papers. This set was then refined by filtering out abstracts and finally full
text filtering. The study selection process is outlined in Figure
\ref{fig:selectionprocess}.

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

A keyword search in online databases was chosen as the means to find potential
primary studies. The databases included in the search are listed in Table
\ref{table:databases}. All databases supported use of complex boolean logic in
searches which allowed us flexibility when constructing the search strings.

@@

Finally, counting 47 papers from the full text filtering step, 3 papers from
preliminary searches, and 2 papers from references, 52 papers were selected
as primary studies.

>>>>

\item
RQ2: How do large scale agile transformations usually proceed?

@@

Before proceeding with the database search a number of preliminary searches were
performed. The purpose of the preliminary searches was to create a benchmark of
potentially relevant papers that should be matched by the actual database
search. We started by examining top ranked hits by trivial keywords that the
more complex final search string might miss. Initial searches were made using
keywords that were as general as possible, including ``agile transformation''
and ``large scale agile''. Secondly, a trial keyword search was done in the
selected databases (listed in table \ref{table:databases}) using the following
search string:

@@

The selection of studies was primarily based on a database search. The initial
step in the database search was constructing a search string which yielded a
reasonably large result set. The search result was then refined in two steps, by
first filtering out abstracts and finally full text filtering. The study
selection process starting from the database search is outlined in figure
\ref{fig:selectionprocess}. The result of the database search was still amended
with some results from the preliminary search and relevant references from all
examined papers.

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Database search as study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

A keyword search in online databases was chosen as the primary means to find
potential primary studies. The databases included in the search are listed in
Table \ref{table:databases}. All databases supported use of complex boolean
logic in searches, which allowed us flexibility in constructing the search
strings.

@@

Finally, counting 47 papers from the full text filtering step, 3 papers from
preliminary searches, and 2 papers from references, 52 papers were selected
as primary studies. The full selection process is illustrated in figure
\ref{fig:selectionprocess_full}.

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process_full.pdf}
    \caption{Full study selection process}
    \label{fig:selectionprocess_full}
  \end{center}
\end{figure}
